Placeholder Title... Something About Delegating Quantum Computations

### 2019-09-23 longoutput.tex
Type up multi-indices for amplification

$$\Rightarrow \frac{1}{D}\braket{\phi|H|\phi}=\E_{\tilde{S}}[\sgn(d_{\tilde{S}})\lambda_{\tilde{S}}]=-p+(1-p)$$
\begin{align*}
	\Rightarrow p&=\frac{1}{2}-\frac{1}{2D}\braket{\phi|H|\phi}\\
	&=\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H|\phi}
\end{align*}

@@

\begin{theorem}
Let $H$ be a local Hamiltonian with the following properties: TODO $\mathcal{G}_{XZ}$???
\begin{itemize}
	\item has $t$ terms
	\item acts on $q$ qubits
	\item Ground state $0$...?
	\item Something something $\frac{3}{4}$?
\end{itemize}
Then, the prover would send the client $n=O(\poly(t))$ copies... TODO
\end{theorem}
\begin{proof}
Let $\set{\ket{\phi_1}, \ket{\phi_2},\ldots,\ket{\phi_q}}$ be the eigenbasis of $H$. Now apply \autoref{ThmXZCheck} to get an algorithm that accepts $\ket{\phi_1}$ with probability $\frac{1}{2}$ and $\ket{\phi_i}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(t)}$ for $i\ne1$. We now decomposite what the prover sends in this basis.
$$\sum_I \alpha_I \ket{\phi_{i_1}}\otimes\ket{\phi_{i_2}}\otimes\ldots\otimes\ket{\phi_{i_q}}$$
We categorize the indices $I$ into three types, based on how many $1$s it contains. First kind contains all $1$s. Second contains so little $1$s that... something something Chernoff bound... And the third kind contains the rest.

$$TODO SOME STATE$$
$$TODO SUM UP COEFFS$$

>>>>

$$\Rightarrow \frac{1}{D}\braket{\phi|H|\phi}=\E_{\tilde{S}}[\sgn(d_{\tilde{S}})\lambda_{\tilde{S}}]=-p+(1-p)$$
\begin{align*}
	\Rightarrow p&=\frac{1}{2}-\frac{1}{2D}\braket{\phi|H|\phi}\\
	&=\frac{1}{2}-\Omega\left(\frac{1}{\poly(T)}\right)\braket{\phi|H|\phi}
\end{align*}

@@

\begin{theorem}
Let $H$ be a local Hamiltonian with the following properties: TODO $\mathcal{G}_{XZ}$???
\begin{itemize}
	\item has $t$ terms
	\item acts on $q$ qubits
	\item Ground state $0$...?
	\item Something something $\frac{3}{4}$?
\end{itemize}
Then, with the input, if honest is $n=O(\poly(t))$... TODO
\end{theorem}
\begin{proof}
Let $\set{\ket{\phi_1}, \ket{\phi_2},\ldots,\ket{\phi_q}}$ be the eigenbasis of $H$. Now apply \autoref{ThmXZCheck} to get an algorithm that accepts $\ket{\phi_1}$ with probability $\frac{1}{2}$ and $\ket{\phi_i}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(t)})$ for $i\ne1$. We now decomposite the input in this basis. We consider the Chernoff bound on... Man these variables are a pain to set up. Let's just say the result is $B$.
Let $\mathcal{I}=\mathbb{Z}_q^n$ be a collection of multi-indices.
We partition the multi-indices into three types.
$$\mathcal{I}=\mathcal{I}_1\sqcup \mathcal{I}_2\sqcup \mathcal{I}_3$$
$$\mathcal{I}_1=\set{(1,1,\ldots,1)}$$
$$\mathcal{I}_3=\set{(j_1, j_2,\ldots,j_n):\abs{\set{j_k=1}}\leq B}$$

Then we can write the input (?) as follows.
$$\alpha\ket{\phi_1^{\otimes n}}+\sum_{J\in\mathcal{I}_2}\beta_J\ket{\phi_J}+\sum_{J\in\mathcal{I}_3}\gamma_J\ket{\phi_J}$$
$$b=\sum_{J\in\mathcal{I}_2}\beta_J^2$$
$$c=\sum_{J\in\mathcal{I}_3}\gamma_J^2$$
